European or American? A re-examination of the transatlantic influence over the IMF

### 2025-04-22 demo/demo.qmd
share csl and bib
Make table in PCA.R (with tinytable)

---
title: European or American? A re-examination of the transatlantic influence over the IMF
header-includes: |
  \AtBeginDocument{\title[European or American]{European or American? A re-examination of the transatlantic influence over the IMF}}
date: last-modified
author:
- name: Dianyi Yang
# - name: Tong Hu // name placeholders subject to change
# - name: Zhenyi Chen
format:
  beamer:
    theme: Madrid
    include-in-header: 
      - text: |
          \definecolor{myblue}{RGB}{0, 113, 187}
          \colorlet{beamer@blendedblue}{myblue}
bibliography: references.bib
csl: extra/apa.csl
---

@@

```{r results}
load('save/regtable.RData')

#t-tests
regtable$`Probit: IMF loan approval`$df.residual <- degrees_of_freedom(
  regtable$`Probit: IMF loan approval`
)

glance_custom.tobit <- function(x, ...) {
  data.frame(
    'equality' = paste0(
      '[',
      '$p=',
      round(lht(x, test = 'F', 'us=eu')[2, 4], 3),
      '$]'
    ),
    'vcov.type' = 'by: Country'
  )
}

glance_custom.fixest <- function(x, ...) {
  data.frame(
    'equality' = paste0(
      '[',
      '$p=',
      round(lht(x, test = 'F', 'us=eu')[2, 4], 3),
      '$]'
    ),
    'vcov.type' = 'by: Country'
  )
}

coefmap <- c(
  'us' = 'US Influence',
  'eu' = 'EU Influence',
  'imf' = 'IMF Influence',
  'lnrgdpnew' = 'GDP',
  'lnrgdpnewsq' = 'GDP$^2$',
  'rgdpchnew' = 'GDPpc',
  'rgdpchnewsquare' = "GDPpc$^2$",
  'growth1new' = 'GDPpc growth',
  'reserv1' = 'Reserves',
  'oecd1' = 'OECD',
  '(Intercept)' = '(Intercept)'
)
gof_map <- list(
  list("raw" = "equality", "clean" = "US=EU", "fmt" = NULL),
  list("raw" = "nobs", "clean" = "$N$", "fmt" = 0),
  list('raw' = 'vcov.type', 'clean' = 'Std.Errors', 'fmt' = NULL)
)
msummary(
  regtable,
  coef_map = coefmap,
  gof_map = gof_map,
  stars = T,
  escape = F,
  output = "kableExtra"
) |>
  kable_styling(latex_options = "scale_down")
```

>>>>

---
title: European or American? A re-examination of the transatlantic influence over the IMF
header-includes: |
  \AtBeginDocument{\title[European or American]{European or American? A re-examination of the transatlantic influence over the IMF}}
date: last-modified
author:
- name: Dianyi Yang
# - name: Tong Hu // name placeholders subject to change
# - name: Zhenyi Chen
format:
  beamer:
    theme: Madrid
    include-in-header: 
      - text: |
          \definecolor{myblue}{RGB}{0, 113, 187}
          \colorlet{beamer@blendedblue}{myblue}
---

@@

```{r results}
load('save/regTable.RData')
resultsTable
```
